---
title: "Demographics Report"
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(readxl)
# remotes::install_github("samuelkaminsky/SKTools")
library(SKTools)
library(plotly)
library(psych)
library(jtools)
library(shiny)
library(lavaan)
library(semPlot)
```

```{r, include=FALSE}
data <- read.csv("Engagement_Pos Qual_2022-05-01_Choice Text.csv", skip = 1) %>% 
  slice(-1)

Demographics <- data %>% 
  select(Response.ID,Duration..in.seconds.,Finished,Location.Latitude,Location.Longitude,Emploment.Status=Which.of.the.following.categories.best.describes.your.employment.status.,
         Industry=Which.of.the.following.categories.best.describes.the.industry.you.work.in.,Size.of.Organization=What.is.the.size.of.the.organization.you.work.for.,
         Work.Arrangement=Which.of.the.following.categories.best.describes.your.current.work.arrangement.,Job.Title=What.is.your.job.title.,
         Job.Managerial.Responsibilities=What.is.the.best.description.of.your.job.s.managerial.responsibilities., Age=Please.indicate.your.age, Education=Please.indicate.your.education.level,
         Gender=To.which.gender.identity.do.you.most.identify.) %>% 
  rename(Time=Duration..in.seconds.)

Engage <- data %>% 
  select(Response.ID,I.am.able.to.concentrate.on.my.work.without.getting.distracted:I.express.enthusiasm.for.my.job.while.at.work.1) %>% 
  unite(.,Item_1,I.am.able.to.concentrate.on.my.work.without.getting.distracted, I.am.able.to.concentrate.on.my.work.without.getting.distracted.1,sep = "",na.rm = T) %>% 
  unite(.,Item_2,Time.passes.quickly.while.I.m.working,Time.passes.quickly.while.I.m.working.1,sep = "", na.rm = T) %>% 
  unite(.,Item_3,I.find.it.difficult.to.mentally.disconnect.from.work, I.find.it.difficult.to.mentally.disconnect.from.work.1, sep = "", na.rm = T) %>% 
  unite(.,Item_4,Thinking.about.work.saps.my.energy, Thinking.about.work.saps.my.energy.1,sep = "",na.rm = T) %>% 
  unite(.,Item_5,I.m.able.to.maintain.good.levels.of.energy.throughout.the.workday,I.m.able.to.maintain.good.levels.of.energy.throughout.the.workday.1,sep = "", na.rm = T) %>% 
  unite(.,Item_6,I.plan.to.stay.with.this.company.as.my.career.advances, I.plan.to.stay.with.this.company.as.my.career.advances.1, sep = "", na.rm = T) %>% 
  unite(.,Item_7,I.believe.this.company.cares.about.my.career.goals, I.believe.this.company.cares.about.my.career.goals.1,sep = "",na.rm = T) %>% 
  unite(.,Item_8,This.organization.challenges.me.to.work.at.my.full.potential,This.organization.challenges.me.to.work.at.my.full.potential.1,sep = "", na.rm = T) %>% 
  unite(.,Item_9,I.enjoy.thinking.about.work.even.when.I.m.not.at.work, I.enjoy.thinking.about.work.even.when.I.m.not.at.work.1, sep = "", na.rm = T) %>% 
  unite(.,Item_10,I.love.starting.my.workday, I.love.starting.my.workday.1,sep = "",na.rm = T) %>% 
  unite(.,Item_11,I.enjoy.spending.time.completing.my.job.tasks,I.enjoy.spending.time.completing.my.job.tasks.1,sep = "", na.rm = T) %>% 
  unite(.,Item_12,I.feel.motivated.to.go.beyond.what.is.asked.of.me.at.work, I.feel.motivated.to.go.beyond.what.is.asked.of.me.at.work.1, sep = "", na.rm = T) %>% 
  unite(.,Item_13,I.feel.proud.of.my.accomplishments.within.this.organization, I.feel.proud.of.my.accomplishments.within.this.organization.1,sep = "",na.rm = T) %>% 
  unite(.,Item_14,My.job.makes.me.feel.like.I.m.part.of.something.meaningful,My.job.makes.me.feel.like.I.m.part.of.something.meaningful.1,sep = "", na.rm = T) %>% 
  unite(.,Item_15,I.have.to.be.reminded.to.take.breaks.while.I.m.at.work, I.have.to.be.reminded.to.take.breaks.while.I.m.at.work.1, sep = "", na.rm = T) %>% 
  unite(.,Item_16,I.never.miss.a.work.deadline, I.never.miss.a.work.deadline.1,sep = "",na.rm = T) %>% 
  unite(.,Item_17,When.work.is.slow.I.find.ways.to.be.productive,When.work.is.slow.I.find.ways.to.be.productive.1,sep = "", na.rm = T) %>% 
  unite(.,Item_18,I.express.enthusiasm.for.my.job.while.at.work, I.express.enthusiasm.for.my.job.while.at.work.1, sep = "", na.rm = T) %>% 
  unite(.,Item_19,I.embrace.challenging.situations.at.work,I.embrace.challenging.situations.at.work.1,sep = "", na.rm = T) %>% 
  unite(.,Item_20,I.speak.positively.about.this.organization.to.others, I.speak.positively.about.this.organization.to.others.1, sep = "", na.rm = T) %>% 
  mutate(across(c("Item_1":"Item_20"),~case_when(str_detect(.,regex("Strongly Disagree"))~"1",
                                                 str_detect(.,regex("Strongle Agree"))~"6",
                                                 str_detect(.,regex("Somewhat Disagree"))~"3",
                                                 str_detect(.,regex("Somewhat Agree"))~"4",
                                                 str_detect(.,regex("Disagree"))~"2",
                                                 str_detect(.,regex("Agree"))~"5"))) %>% 
  mutate(across(c("Item_3","Item_4"),~recode(.,"6"="1","5"="2","4"="3","4"="4","2"="5","1"="6"))) %>% 
  mutate(across(c("Item_1":"Item_20"),~as.numeric(.))) 
```

# Report 

This dashboard will report out all demographic variables we have from our Engagement Survery (Post Qualtric) 2022-05-01.

# Frequences Response {data-navmenu="Engagement"}
```{r}
items <-Engage %>%
  gather(Items, Response,-Response.ID) %>% 
  ggplot(., aes(y = Response, fill= Items)) +
  geom_bar(stat = "count", position = position_dodge(), alpha = .7) +
  theme_nice()
  

ggplotly(items)
```

# CFA {data-navmenu="Engagement"}
```{r, include=FALSE}
substantive <-'
Absorption=~Item_1 + Item_3  + Item_5  + Item_8  + Item_10 + Item_11
Vigor=~Item_14 + Item_16 + Item_17 + Item_19 + Item_21 + Item_22
Dedication=~Item_26 + Item_28 + Item_31 + Item_32 + Item_34 + Item_35
'
fullsub <- lavaan::cfa(substantive, data = Engage); plotfullsub <- fullsub
fullsub <- as.data.frame(fitMeasures(fullsub))
fullsub$rounded <- round(fullsub$`fitMeasures(fullsub)`,2)
t.fullsub <- fullsub %>% 
  select(Substantive=rounded) 
t.fullsub <- as.data.frame(t(t.fullsub[c(3,4,5,23,29,9,10,19),]))        ## Chi-sq, df, RMSEA, SRMR, CFI, TLI, AIC

attiduinal <-'
Cognitive=~Item_1+Item_3+ Item_14 + Item_16 + Item_26 + Item_28
Affective=~Item_5+Item_8+ Item_17 + Item_19 + Item_31 + Item_32
Behavioral=~Item_10+Item_11 + Item_21 + Item_22 + Item_34 + Item_35
'
fullatt <- lavaan::cfa(attiduinal, data = Engage); plotfullatt <- fullatt
fullatt <- as.data.frame(fitMeasures(fullatt))
fullatt$rounded <- round(fullatt$`fitMeasures(fullatt)`,2)

```

# Employeement Status {data-navmenu="Indicators"}

```{r}
es <-Demographics %>% 
  select(Emploment.Status) %>% 
  frequencies(perc=T) %>% 
  ggplot(., aes(x = value, y = perc, fill= value)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = .7) +
  scale_fill_manual(values = c("#00c3e0", "#002046", "#F8BA4E", "#FFA28F", "#9CE8F2", "gray")) +
  theme_nice()
  

ggplotly(es)
```

# Industry {data-navmenu="Indicators"}

```{r}
i <-Demographics %>% 
  select(Industry) %>% 
  frequencies(perc=T) %>% 
  ggplot(., aes(x = value, y = perc, fill= value)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = .7) +
  theme_nice()
  

ggplotly(i)
```

# Size of Organization {data-navmenu="Indicators"}

```{r}
so <-Demographics %>% 
  select(Size.of.Organization) %>% 
  frequencies(perc=T) %>% 
  ggplot(., aes(x = value, y = perc, fill= value)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = .7) +
  theme_nice()
  

ggplotly(so)
```

# Gender {data-navmenu="Biodata"}
```{r}
gen <- Demographics %>% 
  select(Gender) %>% 
  frequencies(perc=T) %>% 
  ggplot(., aes(x = value, y = perc, fill= value)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = .7) +
  theme_nice()
  

ggplotly(gen)
```

# Age {data-navmenu="Biodata"}
```{r}
age <- Demographics %>% 
  select(Age) %>% 
  frequencies(perc=T) %>% 
  ggplot(., aes(x = value, y = perc, fill= value)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = .7) +
  theme_nice()
  

ggplotly(age)
```

# Education {data-navmenu="Biodata"}
```{r}
ed <- Demographics %>% 
  select(Education) %>% 
  frequencies(perc=T) %>% 
  ggplot(., aes(x = value, y = perc, fill= value)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = .7) +
  theme_nice()
  

ggplotly(ed)
```